RD design analysis

### 2024-06-09 analysis/RD design analysis.Rmd
modified:   analysis/RD design analysis.Rmd 	new file:   analysis/RD-design-analysis.log 	new file:   analysis/RD-design-analysis.tex 	new file:   analysis/RD_Plot_1st_Order.pdf 	new file:   analysis/RD_Plot_2nd_Order.pdf 	new file:   analysis/RD_Plot_3rd_Order.pdf 	new file:   analysis/donut_robust.tex 	new file:   archive/RD design archived.Rmd 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new

```{r}
# these are the packages that we need to import
library(haven)
library(ggplot2)
library(dplyr)
library(rdrobust)
library(plm)
library(pander) # this is for table showing
library(latex2exp) # this is to export it
```

```{r}
# need to place data on the base directory
data <- read_dta("../template.dta")
panel_data <- pdata.frame(data, index = c("id", "year"))
panel_data$L_jiadian <- lag(panel_data$jiadian, 1)
panel_data$L_kind <- lag(panel_data$kind, 1)
panel_data$L_hotel <- lag(panel_data$hotel, 1)
panel_data$L_shop_mall <- lag(panel_data$shop_mall, 1)
panel_data$L_museum <- lag(panel_data$museum, 1)
panel_data$L_old <- lag(panel_data$old, 1)
panel_data$L_ktv <- lag(panel_data$ktv, 1)
panel_data$L_mid <- lag(panel_data$mid, 1)
panel_data$L_prim <- lag(panel_data$prim, 1)
panel_data$L_west_food <- lag(panel_data$west_food, 1)
panel_data$L_super <- lag(panel_data$super, 1)
panel_data$L_sub <- lag(panel_data$sub, 1)
panel_data$L_park <- lag(panel_data$park, 1)
```

@@

```{r}
result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
                   c = 0.41, covs = panel_data[, control_variables],
                   p = 1) # first using default clustering
```

```{r}
result
```

```{r}
pander(cbind(result$coef, result$pv))
```

```{r}
result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
                   c = 0.41,
                   p = 1) # first using default clustering
```

```{r}
result
```

```{r}
pander(cbind(result$coef, result$pv))
```

```{r}
result
```

note that the figure only shows points that are within the bandwidth, the whole points are shown in Appendix of the paper.

```{r}
h = 0.095
cutoff = 0.41
running_var = panel_data$nearest_store_distances

@@

par(mfrow=c(3,1))
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 1,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")

rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 2,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")

rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 3,
       title = "RD-plot",
       x.label = "nearest distance to lianjia's stores",
       y.label = "lianjia's income in the community")
```

checkings:

@@

@@

```{r}
donut_width <- 0.015
panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                 panel_data$nearest_store_distances <= (cutoff + donut_width)),]
result_donut <- rdrobust(y = panel_data_donut$ln_income, 
                         x = panel_data_donut$nearest_store_distances, 
                         c = cutoff,  covs = panel_data_donut[, control_variables],
                        p = 1, h = 0.095, b = 0.185)
pander(cbind(result_donut$coef, result_donut$pv))
print(result_donut)
```

```{r}

library(rdd)

# Give it the running variable and the cutpoint
# it will automatically produce a plot and select the number of bins and the bandwidth
# The output will be the p-value for the presence of a discontinuity
DCdensity(panel_data$nearest_store_distances, cutpoint = 0.41, bw = 0.066, verbose = TRUE, plot = FALSE)
```

```{r}
library(rdd)

# Give it the running variable and the cutpoint
# it will automatically produce a plot and select the number of bins and the bandwidth
# The output will be the p-value for the presence of a discontinuity
DCdensity(panel_data$nearest_store_distances, cutpoint = 0.41, bw = 0.095, verbose = TRUE, plot = FALSE)
```

@@

```{r}
for (validation in testing_variables) {
  rd_result <- rdrobust(y = panel_data[[validation]], x = panel_data$nearest_store_distances
                        , c = 0.41, h = 0.066, b = 0.135)
  cat("Covariate:", validation, "\n")
  print(summary(rd_result))
  cat("\n\n")

}
```

>>>>

```{r}
# these are the packages that we need to import
library(haven)
library(rdd)
library(ggplot2)
library(dplyr)
library(rdrobust)
library(plm)
library(xtable)
library(pander) # this is for table showing
library(latex2exp) # this is to export it
setwd("E:/umich/RealEstateBrokerage-main")
# need to place data on the base directory
data <- read_dta("template.dta")
working_directory <-"E:/umich/RealEstateBrokerage"
```

```{r}
panel_data <- pdata.frame(data, index = c("id", "year"))
panel_data$L_jiadian <- lag(panel_data$jiadian, 1)
panel_data$L_kind <- lag(panel_data$kind, 1)
panel_data$L_hotel <- lag(panel_data$hotel, 1)
panel_data$L_shop_mall <- lag(panel_data$shop_mall, 1)
panel_data$L_museum <- lag(panel_data$museum, 1)
panel_data$L_old <- lag(panel_data$old, 1)
panel_data$L_ktv <- lag(panel_data$ktv, 1)
panel_data$L_mid <- lag(panel_data$mid, 1)
panel_data$L_prim <- lag(panel_data$prim, 1)
panel_data$L_west_food <- lag(panel_data$west_food, 1)
panel_data$L_super <- lag(panel_data$super, 1)
panel_data$L_sub <- lag(panel_data$sub, 1)
panel_data$L_park <- lag(panel_data$park, 1)
```

@@

```{r}
h = 0.066
cutoff = 0.41
running_var = panel_data$nearest_store_distances

@@

# Export the first RD plot to its own PDF file
pdf("RD_Plot_1st_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 1,
       title = "RD-plot 1st order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community")
dev.off() # Close the PDF device

# Export the second RD plot to its own PDF file
pdf("RD_Plot_2nd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 2,
       title = "RD-plot 2nd order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community")
dev.off() # Close the PDF device

# Export the third RD plot to its own PDF file
pdf("RD_Plot_3rd_Order.pdf", width = 8, height = 4) # Adjust the width and height as needed
rdplot(y = filtered_data$ln_income, 
       x = filtered_data$nearest_store_distances, 
       c = cutoff, nbins = 40, p = 3,
       title = "RD-plot 3rd order polynomial",
       x.label = "Nearest distance to Lianjia's stores",
       y.label = "Log of income in the community")
dev.off() # Close the PDF device
```

```{r}
bw_methods <- c("mserd", "cerrd")
kernel_list <- c("uniform", "triangular")
results_list <- list()
counter <- 1
for (bw_method in bw_methods) {
    for (kernel_in in kernel_list){
        result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, 
                     c = 0.41,
                     p = 1, 
                     bwselect = bw_method, kernel = kernel_in)

        effective_obs <- sum(result$N_h)

        results_list[[counter]] <- data.frame(
        Method = bw_method,
        Kernel = kernel_in,
        Estimate = format(result$coef[1], digits = 3, scientific = FALSE),
        SE = format(result$se[1], digits = 3, scientific = FALSE),
        Z = format(result$z[1], digits = 3, scientific = FALSE),
        PValue = format(result$pv[1], digits = 3, scientific = FALSE),
        Bandwidth = format(result$bws[1], digits = 3, scientific = FALSE),
        EffectiveObs = effective_obs
    )
        counter <- counter + 1
    }
}
results <- do.call(rbind, results_list)
latex_code <- print(xtable(results, 
                           caption = "RD Estimates with Different Bandwidth Selection Methods and Kernels", 
                           label = "tab:rd_bandwidth_kernel_results"), 
                    include.rownames = FALSE, 
                    type = "latex",
                    print.results = FALSE)
write(latex_code, file = paste(working_directory , "result_tables/rdd_result_summary.tex", sep='/'))
print(results)
```

# checkings:

@@

## Donut Hole Test

@@

```{r}
perform_rd_analysis <- function(cutoff, donut_width, h, b) {
  # select the data that we need
  panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                   panel_data$nearest_store_distances <= (cutoff + donut_width)),]
  # run the rdrobust result
  result_donut <- rdrobust(y = panel_data_donut$ln_income, 
                           x = panel_data_donut$nearest_store_distances, 
                           c = cutoff,
                           p = 1, h = h, b = b)
  # return the coefficient and the p value
  conventional <- c("Conventional", result_donut$coef[1, 1], result_donut$se[1, 1], result_donut$pv[1, 1])
  bias_corrected <- c("Bias-Corrected", result_donut$coef[2, 1], result_donut$se[2, 1], result_donut$pv[2, 1])
  robust <- c("Robust", 
              format(result_donut$coef[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$se[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$pv[3, 1], digits = 3, scientific = FALSE))

  # combine the results
  result_table <- rbind(conventional, bias_corrected, robust)
  colnames(result_table) <- c("Method", "Coef", "SE", "p-value")
  return(result_table)
}

cutoff = 0.41
donut_widths <- c(0.01, 0.0125, 0.015, 0.0175, 0.02, 0.0225, 0.025)
results <- list()

for (donut in donut_widths) {
  result <- perform_rd_analysis(cutoff, donut, 0.066, 0.135)
  results[[paste0("donut_", donut)]] <- result
}

```

```{r}
perform_rd_analysis <- function(cutoff, donut_width, h, b) {
  # select the data that we need
  panel_data_donut <- panel_data[!(panel_data$nearest_store_distances >= (cutoff - donut_width) & 
                                   panel_data$nearest_store_distances <= (cutoff + donut_width)),]
  # run the rdrobust result
  result_donut <- rdrobust(y = panel_data_donut$ln_income, 
                           x = panel_data_donut$nearest_store_distances, 
                           c = cutoff, covs = panel_data_donut[, control_variables],
                           p = 1, h = h, b = b)
  # return the coefficient and the p value
  conventional <- c("Conventional", result_donut$coef[1, 1], result_donut$se[1, 1], result_donut$pv[1, 1])
  bias_corrected <- c("Bias-Corrected", result_donut$coef[2, 1], result_donut$se[2, 1], result_donut$pv[2, 1])
  robust <- c("Robust", 
              format(result_donut$coef[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$se[3, 1], digits = 3, scientific = FALSE), 
              format(result_donut$pv[3, 1], digits = 3, scientific = FALSE))

  # combine the results
  result_table <- rbind(conventional, bias_corrected, robust)
  colnames(result_table) <- c("Method", "Coef", "SE", "p-value")
  return(result_table)
}

cutoff = 0.41
donut_widths <- c(0.01, 0.0125, 0.015, 0.0175, 0.02, 0.0225, 0.025)
results_with_control <- list()

for (donut in donut_widths) {
  result <- perform_rd_analysis(cutoff, donut, 0.066, 0.135)
  results_with_control[[paste0("donut_", donut)]] <- result
}
```

```{r}
# with controls
combined_results_with_control <- do.call(rbind, lapply(names(results_with_control), function(donut) {
  result <- results_with_control[[donut]]
  robust_result <- result[result[, "Method"] == "Robust", ]
  data.frame(Donut_Width = donut, Method = robust_result[1], Coef = robust_result[2], SE = robust_result[3], p_value = robust_result[4])
}))
colnames(combined_results_with_control) <- c("Donut Width", "Method", "Coef", "SE", "p-value")

# without controls
combined_results <- do.call(rbind, lapply(names(results), function(donut) {
  result <- results[[donut]]
  robust_result <- result[result[, "Method"] == "Robust", ]
  data.frame(Donut_Width = donut, Method = robust_result[1], Coef = robust_result[2], SE = robust_result[3], p_value = robust_result[4])
}))
colnames(combined_results) <- c("Donut Width", "Method", "Coef", "SE", "p-value")

merged_results <- merge(combined_results_with_control, combined_results, by = c("Donut Width", "Method"))
merged_results_df <- as.data.frame(merged_results)

colnames(merged_results_df) <- c("Donut Width", "Method", "Coef", "SE", "p-value", "Coef", "SE", "p-value")

# print as a latex table
latex_code <- print(xtable(merged_results_df, 
                           caption = "RD Analysis Donut RD Results with and without Controls", 
                           label = "tab:rd_robust_results"), 
                    include.rownames = FALSE, 
                    type = "latex",
                    print.results = FALSE)

latex_code <- gsub("\\\\begin\\{tabular\\}\\{llllllll\\}\n  \\\\hline\n", 
                   "\\\\begin{tabular}{llllllll}\n  \\\\hline\n &  & \\\\multicolumn{3}{c}{Without Control} & \\\\multicolumn{3}{c}{With Control} \\\\\\\\\n", 
                   latex_code)

latex_code <- gsub("\\\\end\\{tabular\\}", "\\\\end{tabular}\nNote that the cutoff is 0.41, the main bandwidth is 0.066 and the bias bandwidth is 0.135.", latex_code)

write(latex_code, file = paste(working_directory , "result_tables/donut_robust.tex", sep='/'))
```

## McCrary Sorting Test

```{r}
# Give it the running variable and the cutpoint
# it will automatically produce a plot and select the number of bins and the bandwidth
# The output will be the p-value for the presence of a discontinuity
DCdensity(filtered_data$nearest_store_distances, cutpoint = 0.41, bw = 0.066, verbose = TRUE, plot = FALSE)
DCdensity(panel_data$nearest_store_distances, cutpoint = 0.41, bw = 0.066, verbose = TRUE, plot = FALSE)
```

## PlaceBo Test

@@

```{r}
testing_variables <- c("pop", "light", "price_concession", "ln_end_price", "ln_nego_changes", "ln_watch_time", "green_ratio", "bedroom", "ln_watch_people", "living_room", "ln_negotiation_period", "museum", "kind", "mid", "sub", "house_age", "total_building")

results_list <- list()

counter <- 1

for (validation in testing_variables) {
  rd_result <- rdrobust(y = panel_data[[validation]], x = panel_data$nearest_store_distances,
                        c = 0.41, h = 0.066, b = 0.135,
                        bwselect = "mserd", kernel = "triangular")

  # 提取有效观测值数量并相加
  effective_obs <- sum(rd_result$N_h)

  # 提取结果并存储到列表中
  results_list[[counter]] <- data.frame(
    Covariate = validation,
    Estimate = format(rd_result$coef[1], digits = 3, scientific = FALSE),
    SE = format(rd_result$se[1], digits = 3, scientific = FALSE),
    Z = format(rd_result$z[1], digits = 3, scientific = FALSE),
    PValue = format(rd_result$pv[1], digits = 3, scientific = FALSE),
    Bandwidth = format(rd_result$bws[1], digits = 3, scientific = FALSE),
    EffectiveObs = effective_obs
  )
  counter <- counter + 1
}

results <- do.call(rbind, results_list)

latex_code <- print(xtable(results, 
                           caption = "Placebo Test Results for Different Covariates", 
                           label = "tab:placebo_test_results"), 
                    include.rownames = FALSE, 
                    type = "latex",
                    print.results = FALSE)
write(latex_code, file = paste(working_directory , "result_tables/rdd_placebo_test.tex", sep='/'))
print(results)

```

## Cutoff Point movement

The movement of the cutoff point should make the estimation non-significant

```{r}
cutoffs_width <- c(0.15, 0.2, 0.25, 0.30, 0.35, 0.50, 0.65, 0.7)

results_list <- list()
counter <- 1
for (cutoff in cutoffs_width) {
  # rd_result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances, c = cutoff, h = 0.066, b = 0.135, bwselect = "mserd", kernel = "triangular")
  rd_result <- rdrobust(y = panel_data$ln_income, x = panel_data$nearest_store_distances,
                        c = cutoff)

  # 提取有效观测值数量并相加
  effective_obs <- sum(rd_result$N_h)
  # 提取结果并存储到列表中
  results_list[[counter]] <- data.frame(
    Cutoff = cutoff,
    Estimate = format(rd_result$coef[1], digits = 3, scientific = FALSE),
    SE = format(rd_result$se[1], digits = 3, scientific = FALSE),
    Z = format(rd_result$z[1], digits = 3, scientific = FALSE),
    PValue = format(rd_result$pv[1], digits = 3, scientific = FALSE),
    Bandwidth = format(rd_result$bws[1], digits = 3, scientific = FALSE),
    EffectiveObs = effective_obs
  )
  counter <- counter + 1
}
results <- do.call(rbind, results_list)

latex_code <- print(xtable(results, 
                           caption = "Placebo Test Results for Different Cutoff Point", 
                           label = "tab:movement_cutoff"), 
                    include.rownames = FALSE, 
                    type = "latex",
                    print.results = FALSE)
write(latex_code, file = paste(working_directory , "result_tables/movement_cutoff.tex", sep='/'))
print(results)
```
